Psychological Needs During Intergroup Contact

### 2022-01-10 manuscript.tex
figures added

>>>>

\begin{figure}
  \caption{Contact Hypothesis}
  \begin{subfigure}{\textwidth}
    \caption{}
    \centering\includegraphics[width=0.75\textwidth]{Figures/forestBootstrappedGeneralLm.png}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
    \caption{}
    \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricFEGeneralLmer.png}
  \end{subfigure}
  \caption*{Note: \\
  (a) summary of regression results from the aggregated contact and interaction quality data.\\
  (b) summary of mixed models results of the contemporaneous contact effects.\\
  General: Fixed effects meta analytic results are presented for completeness only.}
\end{figure}

\begin{figure}
  \caption{Core Need Fulfillment}
  \begin{subfigure}{\textwidth}
    \caption{}
    \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryQualityCore.png}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
    \caption{}
    \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryAttitudeCore.png}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
    \caption{}
    \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryAttitudeCoreQuality.png}
  \end{subfigure}
  \caption*{Note: \\
  (a) Core Need Fulfillment predicting Interaction Quality.\\
  (b) Core Need Fulfillment predicting Outgroup Attitudes.\\
  (c) Core Need Fulfillment and Interaction Quality predicting Outgroup Attitudes.\\
  General: Fixed effects meta analytic results are presented for completeness only.}
\end{figure}

\begin{figure}
  \caption{Robustness Analyses}
  \begin{subfigure}{\textwidth}
    \caption{}
    \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustContact.png}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
    \caption{}
    \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustSDT.png}
  \end{subfigure}
  \caption*{Note: \\
  (a) Need Fulfillment and Intergroup Contact predicting Outgroup Attitudes (full sample).\\
  (b) Core Need Fulfillment predicting Outgroup Attitudes, while controlling for self-determination theory needs (intergroup contact sample).\\
  General: Fixed effects meta analytic results are presented for completeness only.}
\end{figure}
